Approximation as Differentiation

### 2025-04-01 notes/sec/some-categories-with-biproducts.tex
biadditive -> bilinear seems more common.

\begin{definition}[Vector space over a field $F$]
Suppose $F$ a field with addition of elements written $a + b$ and multiplication written $a \mult b$. Then a
\emph{vector space $V = (V, +, \mult)$ over $F$} (overloading $+$ and $\mult$) is a set $V$ equipped with
addition of vectors $+: V^2 \to V$ and scalar multiplication $\mult: F \times V \to V$ where $(V,+)$ is an
abelian group (with identity element $0_V$ and additive inverse $-v$ for any $v \in V$) and the vector
operations are compatible with the field operations in that the following equations hold:
\begin{itemize}
\item $1 \mult v = v$
\item $(a \mult b) \mult v = a \mult (b \mult v)$
\item $(a + b) \mult v = (a \mult v) + (b \mult v)$
\item $a \mult (u + v) = (a \mult u) + (b \mult v)$
\end{itemize}
\end{definition}

Up to isomorphism a finite-dimensional vector space over $F$ of dimension $n \in \Nat$ is $(F^n, +, \mult)$
with $+$ and $\mult$ defined component-wise. Define $\FdVect_F$ to be the category where
\begin{itemize}
\item the objects are natural numbers $n$ paired with an $n$-dimensional vector space $F^n$
\end{itemize}

>>>>

\begin{definition}[Vector space over a field]
Suppose $F$ a field with addition of elements written $a + b$ and multiplication written $a \mult b$. Then a
\emph{vector space $V = (V, +, \mult)$ over $F$} (overloading $+$ and $\mult$) is a set $V$ equipped with
addition of vectors $+: V^2 \to V$ and scalar multiplication $\mult: F \times V \to V$ where $(V,+)$ is an
abelian group (with identity element $0_V$ and additive inverse $-v$ for any $v \in V$) and the vector
operations are compatible with the field operations in that the following equations hold:
\begin{itemize}
\item $1 \mult v = v$
\item $(a \mult b) \mult v = a \mult (b \mult v)$
\item $(a + b) \mult v = (a \mult v) + (b \mult v)$
\item $a \mult (u + v) = (a \mult u) + (b \mult v)$
\end{itemize}
\end{definition}

Up to isomorphism a finite-dimensional vector space over $F$ of dimension $n \in \Nat$ is $(F^n, +, \mult)$
with $+$ and $\mult$ defined component-wise. Define $\FinVect_F$ to be the category where
\begin{itemize}
\item objects $V, W$ are natural numbers $n$ paired with an $n$-dimensional vector space $F^n$
\item morphisms $f: V \to W$ are functions $f$ satisfying $f(u + v) = f(u) + f(v)$ and $f(a \mult v) = a \mult f(v)$.
\end{itemize}

$\FinVect_F$ is $\Ab$-enriched (and therefore $\CMon$-enriched). For any $V, W$ we have that $\FinVect_F(V,W)$
is an abelian group, where:
\begin{enumerate}
\item $0_{V,W}(v) = 0_W$
\item $(f + g)(v) = f(v) + g(v)$
\item $(-f)(v) = -f(v)$
\end{enumerate}
\noindent with composition bilinear by (2) and the fact that addition of morphisms acts component-wise.
